DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2023-06-28 manuscript/manuscript-1st-submission.Rmd
add updated files for review submission

In ecology and conservation biology, incorporating at least some data on lineage divergence times represents a relevant improvement for testing alternative hypothesis using phylogenetic distance [@Webb2008].
Hence, DateLife's workflow features different ways of estimating node ages in the absence of calibrations and branch length information for certain taxa.
"Making up" branch lengths is a common practice in scientific publications: @Jetz2012, created a chronogram of all 9, 993 bird species, where 67% had molecular data and the rest was simulated; @rabosky2018inverse created a chronogram of 31, 536 ray-finned fishes, of which only 37% had molecular data; @smith2018constructing constructed a chronogram of 353, 185 seed plants where only 23% had molecular data.

>>>>

In ecology and conservation biology, incorporating at least some data on lineage divergence times represents a relevant improvement for testing alternative hypothesis using phylogenetic distance [@Webb2008].
Hence, DateLife's workflow features different ways of estimating node ages in the absence of calibrations and branch length information for certain taxa.

Making up branch lengths is a common practice in scientific publications: @Jetz2012, created a chronogram of all 9, 993 bird species, where 67% had molecular data and the rest was simulated; @rabosky2018inverse created a chronogram of 31, 536 ray-finned fishes, of which only 37% had molecular data; @smith2018constructing constructed a chronogram of 353, 185 seed plants where only 23% had molecular data.
